Proposal to improve BBC Search through the use of Linked Data

### 2014-04-28 paper.tex
Finished first chapter and made some headway with the second.

@@

This report proposes improvements to the BBC Search product making use
of \emph{Linked Data} \cite{bizer2009linked} and/or the Semantic Web
\cite{berners2001semantic}. I hope to be able to demonstrate five tangible
benefits this domain can bring to a search application, namely:

\begin{enumerate}
  \item Further decoupling of BBC applications, which aids scalability,
    maintainability and resilience in many software architectures. \cite{}
  \item Improvements to the search results page that help users determine
    if the results given are relevant via so-called \emph{Rich Snippets}
    that can automatically display some semantic information about a given
    result without the need for manual curation.
  \item User experience and design improvements to the search results
    where semantic properties about the results can drive visual sugar
    and calls to action, which can allow for a more flexible and
    adaptable design without the need to enumerate all ``kinds'' with
    different templates.
  \item Removal of the manual curation of the ``Editor's Choice'' results
    against a given query and replacing it with curated linked data that
    can provide recommended content against queries in a more general
    manner.
  \item Replacement of the manual curation of autocomplete suggestions
    in the \emph{Search Suggest} service -- that suggests full text queries
    as the user types -- with suggestions driven from linked data.
\end{enumerate}

@@

BBC Search is an online product that forms part of the BBC website
to enable users to search for and navigate all areas of the site using
free-text queries. This might aid visitors who are unable to find their desired
content via other global or site-specific navigation or those who are simply
looking for things that fall below the radar of the latest, greatest or
otherwise promoted content.

@@

The general strategy is to perform
any expensive transformation, expansion or ordering of the indexed
at index time so that query time algorithms may be optimised to
run as quickly as possible. This is an approach that has only
increased in importance as information retrieval systems have moved
from standalone systems (e.g. a catalogue search situated within
a library used by a handful of users at once) to web-based
searches across a far larger corpus with tens or even hundreds of
users submitting queries in a single second.

@@

The Search application needs to read in or receive metadata about
BBC content from a variety of sources and then needs to serve
a diverse set of use cases. \cite{fenning2014applicability} The
need to integrate against different data sources and funnel
that information into a common set of search indexes can
typically be seen as an \emph{enterprise integration}
problem. Architectural patterns have been developed, tested and
implemented in a large number of enterprises to synchronise,
transform and normalise data. Such patterns are notably
summarised by Hohpe and Woolf\cite{hohpe2004enterprise}.

Some of the data is fairly flat, textual content such as articles and some
information -- such as programmes -- is very structured (e.g. programmes,
series, episodes, times of broadcast, channel on which they are broadcast,
what times they are available to watch on iPlayer, what kinds of devices
are permitted by rights to watch them on iPlayer). This has challenges
for providing a consistent and meaningful user experience across such
a heterogeneous mix of content.

We can achieve some uniformity of the data by building a single, common
API through which all content is fed into the Search application. However,
it varies based on practicalities whether
work is done by the owners of the content to send content to the API
or whether the developers of the Search application need to integrate
existing feeds via an adapter pattern. Some pages on the BBC website no
longer have a dedicated team maintaining them and can sometimes only
be discovered via a web crawl as an external search engine would do. A lot
of metadata about content also lives in a diverse range of databases and
content management systems, which can be collectively described as part
of the so-called \emph{deep web}. \cite{}

@@

% Do we need this?
Concepts central to the information retrieval domain such as creating
tokenisation, stemming, lemmatisation and relevance
algorithms can normally be delegated to
third party proprietary or free software. It is still useful however
for developers of full search application to be aware of these concepts even
if their implementation is abstracted away. Tokenisation, stemming and
lemmatisation are index time concerns, the full definitions of which
are out of scope for this report. In short, we want a search application
to understand individual words within an article and to understand that, for
example, ``mice'' and ``mouse'' are approximately the same word as well
as verb forms like ``swim'', ``swam'', ``swum'' and ``swimming'' all being
equivalent in the context of keyword retrieval.

@@

\begin{equation}
  precision = \quot{|{relevant documents}\and{retrieved documents}|}{|{retrieved documents}|}
\end{equation}

\begin{equation}
  recall = \quot{|{relevant documents}\and{retrieved documents}|}{|{relevant documents}|}
\end{equation}

@@

Note that a system could trivially maximise recall by always returning all
results, but such a system would perform poorly in terms of precision. A
measure known as \emph{F-measure} was derived by van Rijsbergen \cite{} which
balances precision recall based on preferring recall over precision \beta
times:

% TODO: equation

There are other measures such as average precision and average mean precision
that take into account ordering of results and the average over multiple
queries respectively. A successful algorithm or third party search engine
application can be evaluated quantitatively by these measures and more. A more
qualitatively summary from the perspective of the end users could be:

@@

Editorial staff thus have control over a curation system that manifests
as an \emph{Editor's Choice} feature that will ensure the top one to three
results for popular queries link to manually-chosen pages deemed as the most
relevant pages for those queries. For instance, a search for a city such
as Coventry might naturally return recent news articles that mention the
city (since news results are biased towards more recent articles over older
ones), but the Editor's Choice links on top of the so-called \emph{organic
results} can persistently offer users links for common use cases such as
the BBC Weather page for Coventry.

@@

One challenge for the querying of a search application is to be tolerant
of variable quality of user-entered queries. Many users of web search
engines may give ambiguously short queries, overly long queries with (where
it can be hard for a machine to pick out the important keywords amongst
less important words or stop words) or simply use incorrect spelling.

\chapter{State of the Art in Linked Data}
\label{stateoftheart}

@@

\bibliographystyle{cell}
\bibliography{bibtex}

>>>>

\usepackage{mathtools}

@@

This report proposes improvements to the BBC Search product making use
of \emph{Linked Data}\cite{bizer2009linked} and/or the Semantic
Web\cite{berners2001semantic}. I hope to be able to demonstrate five tangible
benefits this domain can bring to a search application, namely:

\begin{enumerate}
  \item Further decoupling of BBC applications, which aids scalability,
    maintainability and resilience in many software architectures.\cite{}
  \item Improvements to the search results page that help users determine
    if the results given are relevant via so-called
    \emph{Rich Snippets}\cite{goel2009introducing}
    that can automatically display some semantic information about a given
    result without the need for manual curation.
  \item User experience and design improvements to the search results
    where semantic properties about the results can drive visual decoration
    and calls to action, which can allow for a more flexible and
    adaptable design without the need to enumerate all ``kinds'' with
    different templates.
  \item Removal of the manual curation of the ``Editor's Choice'' results
    against a given query and replacing it with curated linked data that
    can provide recommended content against queries in a more general
    manner.
  \item Replacement of the manual curation of autocomplete suggestions
    in the \emph{Search Suggest} service -- that suggests full text queries
    as the user types -- with suggestions driven from linked data.
\end{enumerate}

@@

BBC Search is an online product that forms part of the BBC website
to enable users to search for and navigate all areas of the site using
free text queries. This might aid visitors who are unable to find their desired
content via other global or site-specific navigation or those who are simply
looking for things that fall below the radar of the latest, greatest or
otherwise promoted content.

@@

The general strategy is to perform
any expensive transformation, expansion or ordering of data
at index time so that query time algorithms may be optimised to
run as quickly as possible. This is an approach that has only
increased in importance as information retrieval systems have moved
from standalone systems (e.g. a catalogue search situated within
a library used by a handful of users at once) to web-based
searches across a far larger corpus with tens or even hundreds of
users submitting queries in a single second.

@@

The Search application needs to read in or receive metadata about
BBC content from a variety of sources and then needs to serve
a diverse set of use cases.\cite{fenning2014applicability} The
need to integrate against different data sources and funnel
that information into a common set of search indexes can
typically be seen as an \emph{enterprise integration}
problem. Architectural patterns have been developed, tested and
implemented in a large number of enterprises to synchronise,
transform and normalise data. Such patterns are notably
summarised by Hohpe and Woolf.\cite{hohpe2004enterprise}

Some of the data is fairly flat, textual content such as articles and some
information -- such as programmes -- is very structured (e.g. programmes,
series, episodes, times of broadcast, channel on which they are broadcast,
what times they are available to watch on iPlayer, what kinds of devices
are permitted by rights to watch them on iPlayer). There are challenges
in providing a consistent and meaningful user experience across such
a heterogeneous mix of content.

We can achieve some uniformity of the data by building a single, common
API through which all content is fed into the Search application. However,
some integration work needs to be
done by either the owners of the content to send content to the API
or the developers of the Search application, who can integrate
existing feeds via an adapter pattern.

Some pages on the BBC website no
longer have a dedicated team maintaining them and can sometimes only
be discovered via a web crawl as an external search engine would do. A lot
of metadata about content also lives in a diverse range of databases and
content management systems, which can be collectively described as part
of the so-called \emph{deep web}.\cite{}

@@

@@

\begin{displaymath}
  \textbf{precision} = \frac{
    |\text{relevant documents} \cap \text{retrieved documents}|
  }{
    |\text{retrieved documents}|
  }
\end{displaymath}

\begin{displaymath}
  \textbf{recall} = \frac{
    |{relevant documents} \cap \text{retrieved documents}|
  }{
    |\text{relevant documents}|
  }
\end{displaymath}

@@

Note that a system could trivially maximise recall by always returning all
results, but such a system would perform poorly in terms of precision. A
measure known as \emph{F-measure} was derived by van Rijsbergen
\cite{rijsbergen1979information} which
balances precision recall based on preferring recall over precision $\beta$
times:

$$F_\beta = (1 + \beta^2) \cdot \frac{\mathrm{precision} \cdot \mathrm{recall} }{ \beta^2 \cdot \mathrm{precision} + \mathrm{recall}}$$

There are other measures such as average precision and average mean precision
that take into account ordering of results and the average over multiple
queries respectively. A successful algorithm or third party search engine
application can be evaluated quantitatively by these measures and more. A more
qualitative summary from the perspective of the end users could be:

@@

Editorial staff thus have control over a curation system that manifests
as an \emph{Editor's Choice} feature that will ensure the top one to three
results for popular queries link to manually-chosen pages deemed as the most
relevant pages for those queries. For instance, a search for a city such
as \emph{Coventry} might naturally return recent news articles that mention the
city (since news results are biased towards more recent articles over older
ones), but the Editor's Choice links on top of the so-called \emph{organic
results} can persistently offer links for common use cases such as
the BBC Weather page for Coventry.

@@

One challenge for the querying of a search application is to be tolerant
of the variable quality of user-entered queries. Many users of web search
engines may give ambiguously short queries, overly long queries with (where
it can be hard for a machine to pick out the important keywords amongst
less important words or stop words\cite{rajaraman2011data})
or simply use incorrect spelling.

This problem can be ameliorated with a plethora of algorithm
server-side solutions (e.g. spell checking), but a simple solution that
can be implemented on the user interface is an \emph{autocomplete}
or \emph{autosuggest} feature. The former prompts for potential
queries, titles, names, etc. that they may be typing so as to prevent
the need to type the query out in full. The latter feature can go
further to suggest onwards journeys that bypass the need for a
page of search results altogether.

The search box for BBC Search implements an autocomplete
feature -- known
as \emph{Search Suggest} -- whereby
the full names or titles of are suggested to users as they type the first
few characters of their queries. This helps guide users into free text
queries that are more likely to match terms in the indexes and reduces
mismatching due to misspellings or otherwise poorly-formed queries.

The list of suggestions that might surface in this system are
currently chosen and maintained by hand by editorial staff. If a new
concept breaks into the news (such as a notable person becoming notable
for the first time), then a person must enter that term into the system.
Similarly, if something should not be suggested to users any longer
(perhaps for legal reasons or simply because it is no longer a relevant
concept), then it must be amended or removed manually.

This manual maintenance of the suggestion list also leads to a
disconnect between searchable content and suggested queries that might
appear as users type. There is an onus on editorial staff to ensure
that content will be found when a suggested query is used. It might
serve the website users better to find mechanisms by which to generate
a useful set of suggestions from the corpus of content as it is
indexed. The heterogenous nature of BBC content turns this into
further integration work where different business rules are likely required
to generate suggestions from different types of content.

In chapter~\ref{stateoftheart} I will briefly outline some of the state of the
art in the Linked Data domain and start to highlight areas that show
the most promise for improving the four areas of the search application
described in this chapter.

\chapter{Linked Data}
\label{stateoftheart}

\section{Linked Data Principles}

The concept of Linked Data can well be summarised as a representation of
data that follows four principles:\cite{berners2011linked}

\begin{enumerate}
  \item Use URIs to denote things.
  \item Prefer HTTP URIs (i.e. URLs) so that these things can be looked
    up (i.e. \emph{dereferenced}.
  \item When these URIs are dereferenced, provide useful information about
    those things using standards.
  \item Include links to other things (using their URIs) when such
    information is published on the web.
\end{enumerate}

@@

\bibliographystyle{plain}
\bibliography{bibtex}
